---
title: "R Basics"
author: "Divya Sherwani"
date: "June 28, 2021"
output: word_document
---

```{r}
# Defining a variable
x <- 5
x
```

```{r}
# Taking name input from user
y <- readline(prompt = "Enter your name:")
y
```

```{r}
# Taking age input from user
age = as.double(readline(prompt = "Enter age:"))
```

```{r}
# To print a sequence of numbers
1:15
```

```{r}
# Concatenate
a = c(1:15,100)
a
```

```{r}
# Paste
paste("xyz",c(2,5,7,"test",4:5))
```

```{r}
# Sequence
b = seq(1, 20, 2)
```


Functions

```{r}
# Sum Function
num1 = 5
num2 = 7
add = function(num1, num2){
  print(num1+num2)
}
add(num1, num2)
```

For loop

```{r}
# Factorial function
fact = function(n){
  for (i in n){
    if (n ==0 | n==1){
    factorial =  1
    print(factorial)
  }else{
    factorial = factorial(n-1) * n
    print(factorial)
  }
  }
}
n = 4
fact(n)
```


Write a R program to take input from the user (name and age) and display the values.

```{r}
name = readline(prompt="Enter your name:")
age = as.double(readline(prompt = "Enter your age:"))
print(name)
print(age)
```


Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 60 and sum of numbers from 51 to 91. 

```{r}
sequence = seq(20, 50)
mean(20:60)
sum(51:91)
```

Write a R program to create a vector which contains 10 random integer values between -50 and +50.

```{r}
sample(-50:50, 10, replace = TRUE)
```

Write a R program to get the first 10 Fibonacci numbers.


```{r}
sequence = numeric()
fibonacci = function(n){
  for (i in 1:n){
    if (i==1 | i==2){sequence = append(sequence,1)}
    else{sequence = append(sequence, sequence[i-1] + sequence[i-2])}
  }
  print(sequence)
}
fibonacci(10)
```

Write a R program to print the numbers from 1 to 100 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both. 

```{r}
print(1:100)
for (i in 1:100){
  if (i%%3 ==0 & i%%5==0){
    print("FizzBuzz")
  } else if (i%%3==0 & i%%5!=0){
    print("Fizz")
  } else {print("Buzz")}
}
```

Write a R program to extract first 10 english letter in lower case and last 10 letters in upper case and extract letters between 22nd to 24th letters in upper case.

```{r}
letters[1:10]
LETTERS[16:26]
LETTERS[22:24]
```


Write a R program to find the factors of a given number.

```{r}
n = 10
factors = numeric()
factor = function(n){
  for (i in 1:n){
  if (i==0){
    print("No factors")
  } else if (n%%i == 0){
    factors = append(factors,i)
  }
  }
  print(factors)
}
factor(10)
```


Write a R program to find the maximum and the minimum value of a given vector. 

```{r}
a = c(1:10, 200)
a
paste("Minimum value is", min(a))
paste("Maximum value is", max(a))
```



